---
title: "Predictive model for FIFA 20"
output: 
  html_document:
    toc: true
---

# Install packages

```{r eval=FALSE}
install.packages(c("DALEX", "modelStudio", "ingredients", "iBreakDown", "gbm")
```

# Read data

Use the `players_20.csv` data from the kaggle website https://www.kaggle.com/stefanoleone992/fifa-20-complete-player-dataset.
It is available in the `DALEX` package.

```{r warning=FALSE, message=FALSE}
library(DALEX)
data <- fifa
```

# Feature selection

This dataset has 4 potential target variables and one categorical feature.
Let's select only the `value_eur` target and remove the `nationality` feature.

```{r warning=FALSE, message=FALSE}
data$wage_eur <- data$overall <- data$potential <- data$nationality <- NULL
```

# Feature engineering

Target value is skewed. Will be much easier to model sqrt(value).

```{r warning=FALSE, message=FALSE}
data$value_eur <- log10(data$value_eur)
```

# Create a gbm model

Let's use `gbm` library to create a `gbm` model with 250 trees 3 levels deep.

```{r warning=FALSE, message=FALSE}
set.seed(1313)

library("gbm")
model <- gbm(value_eur ~ . , data = data, n.trees = 300, interaction.depth = 4)
```

# Create a DALEX explainer

Let's wrap gbm model into a DALEX explainer.

```{r warning=FALSE, message=FALSE}
explainer <- DALEX::explain(model, 
                            data = data[,-1], 
                            y = 10^data$value_eur, 
                            predict_function = function(m,x) 
                                10^predict(m, x, n.trees = 300),
                            label = 'gbm')
```

# Feature Importance explainer

Calculate Feature Importnace explainer.

```{r warning=FALSE, message=FALSE}
library("ingredients")
fi <- ingredients::feature_importance(explainer, B=15)
plot(fi, max_vars = 9)
```

# Partial Dependency explainer

Calculate Partial Dependency explainer.

```{r warning=FALSE, message=FALSE}
pdp <- ingredients::partial_dependency(explainer, variables = "age")
plot(pdp)
```

# Ceteris Paribus explainer

Calculate Ceteris Paribus explainer.

```{r warning=FALSE, message=FALSE}
new_observation <- data["R. Lewandowski",]

cp <- ingredients::ceteris_paribus(explainer, new_observation = new_observation, variables = "age",
                                   variable_splits = list(age = seq(18,45,0.1)))
plot(cp, subtitle = 'for Robert Lewandowski (GBM model)')
```

# Break Down explainer

Calculate Break Down explainer.

```{r warning=FALSE, message=FALSE}
library("iBreakDown")
bd <- iBreakDown::break_down(explainer, new_observation = new_observation)
plot(bd)

library("ggplot2")
library("scales")
plot(bd, digits = 0, max_features = 10, subtitle = 'for Robert Lewandowski') +  
  scale_y_continuous(labels = dollar_format(suffix = "€", prefix = ""), name = "Estimated value",
                     limits = 1000000*c(1, 75), breaks = 1000000*c(1,25,50,75))


sh <- iBreakDown::shap(explainer, new_observation = new_observation, B=15)
plot(sh, max_features = 9)
```

# modelStudio app

Create a `modelStudio` dashboard.

More resources: https://github.com/ModelOriented/modelStudio

```{r eval = FALSE, warning=FALSE, message=FALSE}
library("modelStudio")

# Use parallelMap to speed up the computation
options(
    parallelMap.default.mode        = "socket",
    parallelMap.default.cpus        = 4,
    parallelMap.default.show.info   = FALSE
)

# Pick observations
fifa_selected <- data[1:40, ]

# Make a studio for the model
fifa20_ms <- modelStudio(
                 explainer, 
                 new_observation = fifa_selected,
                 parallel = TRUE,
                 rounding_function = signif, digits = 5,
                 options = ms_options(
                     #show_boxplot = FALSE,
                     margin_left = 175,
                     margin_ytitle = 110,
                     ms_title = "Interactive Model Studio for ⚽⚽⚽ FIFA 20 ⚽⚽⚽ (GBM model)"
             ))

fifa20_ms

# Save as HTML
r2d3::save_d3_html(fifa20_ms, file = "fifa20_ms.html")

```

