---
title: "Predictive model for FIFA 20"
output: 
  html_document:
    toc: true
---

# Read data

Read the data from the kaggle website https://www.kaggle.com/stefanoleone992/fifa-20-complete-player-dataset.

```{r warning=FALSE, message=FALSE}
library("readr")
fifa20 <- as.data.frame(read_csv("players_20.csv"))
```

# Feature selection

Let's select only features related to player characteristics.

```{r warning=FALSE, message=FALSE}
fifa20_selected <- fifa20[,c(4,5,7,8,11:13,17,25:26,45:78)]
```

# Feature engineering

Value is skewed. Will be much easier to model sqrt(Value).

```{r warning=FALSE, message=FALSE}
fifa20_selected$value_eur <- log10(fifa20_selected$value_eur)

fifa20_selected$team_position <- factor(fifa20_selected$team_position)

fifa20_selected <- na.omit(fifa20_selected)
fifa20_selected <- fifa20_selected[fifa20_selected$value_eur > 0,]
fifa20_selected <- fifa20_selected[!duplicated(fifa20_selected[,1]),]
rownames(fifa20_selected) <- fifa20_selected[,1]
fifa20_selected <- fifa20_selected[,-1]
```

# Create a gbm model

Let's use `gbm` library to create a `gbm` model with 250 trees 3 levels deep.

```{r warning=FALSE, message=FALSE}
set.seed(1313)

library("gbm")
# 4:5 are overall and potential, too strong predictors
fifa_gbm <- gbm(value_eur ~ . , data = fifa20_selected[,-(4:5)], n.trees = 250, interaction.depth = 3)
```

# Create a DALEX explainer

Let's wrap gbm model into a DALEX explainer.

```{r warning=FALSE, message=FALSE}
library("DALEX")

fifa_gbm_exp <- explain(fifa_gbm, 
                        data = fifa20_selected, 
                        y = 10^fifa20_selected$value_eur, 
                        predict_function = function(m,x) 
                          10^predict(m, x, n.trees = 250))
```

# Feature Importance explainer

Calculate Feature Importnace explainer.

```{r warning=FALSE, message=FALSE}
library("ingredients")
fifa_feat <- ingredients::feature_importance(fifa_gbm_exp)
plot(fifa_feat, max_vars = 12)
```

# Partial Dependency explainer

Calculate Partial Dependency explainer.

```{r warning=FALSE, message=FALSE}
fifa20_pd <- ingredients::partial_dependency(fifa_gbm_exp, variables = "age")
plot(fifa20_pd)
```

# Ceteris Paribus explainer

Calculate Ceteris Paribus explainer.

```{r warning=FALSE, message=FALSE}
new_observation <- fifa20_selected["Robert Lewandowski",]

fifa20_cp_pg <- ingredients::ceteris_paribus(fifa_gbm_exp, new_observation = new_observation, variables = "age", variable_splits = list(age = seq(18,45,0.1)))
plot(fifa20_cp_pg)
```

# Break Down explainer

Calculate Break Down explainer.

```{r warning=FALSE, message=FALSE}
library("iBreakDown")
fifa_pg_gbm <- break_down(fifa_gbm_exp, new_observation = new_observation)
plot(fifa_pg_gbm, max_features = 10)

fifa_pg_gbm$label = "Break Down for Robert Lewandowski (GBM model)"

library("ggplot2")
library("scales")
plot(fifa_pg_gbm, digits = 0, max_features = 10) +  
  scale_y_continuous(labels = dollar_format(suffix = "€", prefix = ""), name = "Estimated value", limits = 1000000*c(1,100), breaks = 1000000*c(1,25,50,75,100))
```

# modelStudio app

Calculate modelStudio dashboard.

```{r eval = FALSE}
library("modelStudio")
options(
    parallelMap.default.mode        = "socket",
    parallelMap.default.cpus        = 4,
    parallelMap.default.show.info   = FALSE
)


fifa_selected_40 <- fifa20_selected[c(1:40, 61), ]

fifa20_ms <- modelStudio(fifa_gbm_exp, 
                         new_observation = fifa_selected_40,
                         B = 5, N = 300,
                         parallel = TRUE,
                         options = modelStudioOptions(margin_left = 175, margin_ytitle = 120,
                        ms_title = "Interactive Model Studio for ⚽⚽⚽   FIFA 20 ⚽⚽⚽  (GBM model) "),
                         digits = 0)

fifa20_ms


r2d3::save_d3_html(fifa20_ms, file = "fifa20_ms.html")

```

